\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-13 paper/supplementary.Rnw
Redone fullsub

@@

\section{Descriptive Statistics for Individuals}

\begin{figure}[htbp]
\centering
<<choices, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
full.sub$choice_reason <-sapply(strsplit(as.character(unlist(full.sub$choice_reason)), "[^0-9]+"), "[[", 1)
ggplot(data=full.sub) + geom_bar(aes(x=choice_reason))
choice <- full.sub %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@

\begin{figure}[htbp]
\centering 
<<avscore, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>= 
subjplot <- summarise(group_by(full.sub, subj_id), eval=sum(weights), total = sum(score))
subjplot <- mutate(subjplot, avscore= total/eval)
ggplot(data=subjplot, aes(x=avscore)) + geom_histogram(binwidth=0.05)
@

\begin{figure}[htbp]
\centering
<<multiselect, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, bylineup, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=r, fill=plot), binwidth=0.2) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
ggplot(data=subset(m.lineup, smoothed==1)) + geom_bar(aes(x=r, fill=plot), binwidth=0.2) + facet_wrap(~n)
@

\begin{table}
\caption{Number of selections per lineup evaluation. The subject with the most selections is reported.}
\label{tabattempts}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{attempts}}
\label{attempts}
\end{figure}

@@

\begin{figure}
  \centering
<<residuals, dependson='setup', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
glmm.resid <- subset(prediction, detected==0 | detected==1)
ggplot(data=glmm.resid) + geom_histogram(aes(y=..density.., x=residual), binwidth=2) + labs(x=NULL, y=NULL)
@
  \caption{Histograms of residuals, $\hat{\epsilon}$ for both the scatter plot (left) and the overlaid lines (right). Both appear to be normal, though there are some extreme outliers.}
    \label{residuals}
\end{figure}

>>>>

\title{\bf Supplementary Material: Comparing the Power of Plot Designs to Reveal Correlation

@@

\section{Descriptive Statistics of Evaluations}

\begin{table}[htp]
\caption{The true plot detections / evaluations for each lineup in the data collection. Lineups with the same factor combination are seperated by row. Results ignore multiple selection and any removed evaluations. True plot correlation is on the x axis and t is on the y axis.}
\label{tabeval}
\centering
<<answertables, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
turk.tbl <- select(bylineup, design, smoothed, r, n, correct, evals)
turk.tbl$result <- paste(round(turk.tbl$correct, 0), turk.tbl$evals, sep="/")
turk.tbl <- turk.tbl[order(turk.tbl$r, turk.tbl$n),]
scatter.uns <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==0 & design=="Scatterplot")$result, ncol=8))
scatter.sm <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==1 & design=="Scatterplot")$result, ncol=8))
line.uns <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==0 & design=="Overlaid Lines")$result, ncol=8))
line.sm <- data.frame(c(12, "", "", 24, "", "", 48, "", "", 96, "", ""), matrix(subset(turk.tbl, smoothed==1 & design=="Overlaid Lines")$result, ncol=8))
colnames(scatter.uns) <- c("Unsmoothed Scatterplot", "-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
colnames(scatter.sm) <- c("Smoothed Scatterplot","-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
colnames(line.uns) <- c("Unsmoothed Overlaid Lines","-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
colnames(line.sm) <- c("Smoothed Overlaid Lines","-0.9", "-0.7", "-0.5", "-0.3", "0.3", "0.5", "0.7", "0.9")
kable(scatter.uns, format="latex")
@
\end{table}
\begin{table}
\centering
<<answertables2, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
kable(scatter.sm, format="latex")
@
\end{table}
\begin{table}
\centering
<<answertables3, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
kable(line.uns, format="latex")
@
\end{table}
\begin{table}
\centering
<<answertables4, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
kable(line.sm, format="latex")
@
\end{table}

\begin{figure}[htbp]
\centering
<<choices, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
full$choice_reason <-sapply(strsplit(as.character(unlist(full$choice_reason)), "[^0-9]+"), "[[", 1)
ggplot(data=full.sub) + geom_bar(aes(x=choice_reason))
choice <- full %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@
\caption{Reasons given for plot selection}
\label{reasons}
\end{figure}

\begin{figure}[htbp]
\centering 
<<avscore, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>= 
subjplot <- summarise(group_by(full.sub, subj_id), eval=sum(weights), total = sum(score))
subjplot <- mutate(subjplot, avscore= total/eval)
ggplot(data=subjplot, aes(x=avscore)) + geom_histogram(binwidth=0.05)
@
\caption{Average score of subjects included in modelling}
\label{avscore}
\end{figure}

\begin{figure}[htbp]
\centering
<<multiselect, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, bylineup, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=factor(r), fill=design), binwidth=0.2) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
@
\caption{Characteristics of lineups with at least one subject making multiple selections}
\label{lineupmulti}
\end{figure}

\begin{table}[htp]
\caption{Number of selections per lineup evaluation. The subject with the most selections is reported.}
\label{tabattempts}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{tabattempts}}
\label{attemptshist}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<residuals, dependson='setup', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
glmm.resid <- subset(prediction, detected==0 | detected==1)
ggplot(data=glmm.resid) + geom_histogram(aes(y=..density.., x=residual), binwidth=2) + labs(x=NULL, y=NULL)
@
  \caption{Histograms of residuals, $\hat{\epsilon}$ for both the scatter plot (left) and the overlaid lines (right). Both appear to be normal, though there are some extreme outliers.}
    \label{residuals}
\end{figure}
